``Interestingness'' in Mathematical Theory Exploration

### 2019-05-16 PhDThesis/background_haskell.tex
Headingy things

\subsection{Haskell}
\label{sec:haskell}

@@

even :: Nat -> Bool
even    Z  = True
even (S n) = odd n
  \end{haskell}
  \caption{Haskell code, defining datatypes and functions involving them (note
    that \hs{--} introduces a comment). \hs{Bool} is the Booleans, \hs{Nat} is a
    Peano encoding of the natural numbers and \hs{List t} are polymorphic lists
    with elements of type \hs{t}. Functions are called using whitespace, e.g.
    \hs{f x}, and may be defined by pattern-matching (case analysis) on their
    arguments. \hs{A :: B} is an optional type annotation, stating that value
    \hs{A} has type \hs{B}. \hs{A -> B} is the type of functions from \hs{A} to
    \hs{B}.}
  \label{fig:haskellexample}
\end{figure}

>>>>

\section{Haskell}
\label{sec:haskell}

@@

even :: Nat -> Bool
even    Z  = True
even (S n) = odd n
  \end{haskell}
  \caption{Haskell code, defining datatypes and functions involving them (note
    that \hs{--} introduces a comment). \hs{Bool} is the Booleans, \hs{Nat} is a
    Peano encoding of the natural numbers and \hs{List t} are polymorphic lists
    with elements of type \hs{t}. Juxtaposition denotes a function call, e.g.
    \hs{f x}, and functions may be defined by pattern-matching (case analysis)
    on their arguments. \hs{A :: B} is an optional type annotation, stating that
    value \hs{A} has type \hs{B}. \hs{A -> B} is the type of functions from
    \hs{A} to \hs{B}.}
  \label{fig:haskellexample}
\end{figure}

### 2019-05-16 PhDThesis/bucketing.tex
Fix metadata
Headingy things

\section{The Signature Selection Problem}

@@

\subsection{Background}
\label{sec:background}

@@

\subsection{Clustering}
\label{sec:clustering}

@@

\section{Contributions}
\label{sec:contributions}

@@

\subsection{Experiments}

@@

\item{Sandboxing}: One difficulty with Haskell's packaging infrastructure is
  that all required packages and modules must be provided up-front, usually by
  specification in a Cabal file. Since \textsc{MLSpec} builds signatures
  \emph{dynamically}, depending on the cluster information it is given, we do
  not know what packages it may need. To work around this problem, we evaluate
  these strings of Haskell using a custom library called \texttt{nix-eval}. This
  uses the Nix package manager to obtain all of the required packages and make
  them available to GHC.

@@

\begin{figure}
  \begin{haskell}
(defun fact (n)
  (if (zp n) 1 (* n (fact (- n 1)))))

@@

(defun fib-tail (n)
  (helper-fib n 0 1))
  \end{haskell}
  \caption{Common Lisp functions, both tail-recursive and non-tail-recursive.}
  \label{fig:lisp}
\end{figure}

@@

\begin{equation}\label{fig:coresyntax}
  \begin{split}
    expr\    \rightarrow\ & \CVar\ id                          \\
                       |\ & \CLit\ literal                     \\
                       |\ & \CApp\ expr\ expr                  \\
                       |\ & \CLam\ \mathcal{L}\ expr           \\
                       |\ & \CLet\ bind\ expr                  \\
                       |\ & \CCase\ expr\ \mathcal{L}\ [alt]   \\
                       |\ & \CType                             \\
    id\      \rightarrow\ & \CLocal\       \mathcal{L}         \\
                       |\ & \CGlobal\      \mathcal{G}         \\
                       |\ & \CConstructor\ \mathcal{D}         \\
    literal\ \rightarrow\ & \CLitNum\ \mathcal{N}              \\
                       |\ & \CLitStr\ \mathcal{S}              \\
    alt\     \rightarrow\ & \CAlt\ altcon\ expr\ [\mathcal{L}] \\
    altcon\  \rightarrow\ & \CDataAlt\ \mathcal{D}             \\
                       |\ & \CLitAlt\ literal                  \\
                       |\ & \CDefault                          \\
    bind\    \rightarrow\ & \CNonRec\ binder                   \\
                       |\ & \CRec\ [binder]                    \\
    binder   \rightarrow\ & \CBind\ \mathcal{L}\ expr
  \end{split}
\end{equation}
Where:
\begin{tabular}[t]{l @{ $=$ } l}
  $\mathcal{S}$ & string literals    \\
  $\mathcal{N}$ & numeric literals   \\
  $\mathcal{L}$ & local identifiers  \\
  $\mathcal{G}$ & global identifiers \\
  $\mathcal{D}$ & constructor identifiers
\end{tabular}

>>>>

\chapter{The Signature Selection Problem}

@@

\section{Background}
\label{sec:background}

@@

\section{Clustering}
\label{sec:clustering}

@@

@@

\section{Experiments}

@@

\item{Sandboxing}: One difficulty with Haskell's packaging infrastructure is
  that all required packages and modules must be provided up-front, usually by
  specification in a Cabal file. Since \textsc{MLSpec} builds signatures
  \emph{dynamically}, depending on the cluster information it is given, we do
  not know what packages it may need. To work around this problem, we evaluate
  these strings of Haskell using a custom library called \texttt{nix-eval}. This
  uses the Nix package manager to obtain all of the required packages and make
  them available to GHC, and is described further in
  Appendix~\ref{sec:nix-eval}.

@@

\begin{figure}
  \begin{common-lisp}
(defun fact (n)
  (if (zp n) 1 (* n (fact (- n 1)))))

@@

(defun fib-tail (n)
  (helper-fib n 0 1))
  \end{common-lisp}
  \caption{Common Lisp functions, both tail-recursive and non-tail-recursive.}
  \label{fig:lisp}
\end{figure}

@@

\begin{equation}\label{eq:coresyntax}
  \begin{split}
    expr\    \rightarrow\ & \CVar\ id                          \\
                       |\ & \CLit\ literal                     \\
                       |\ & \CApp\ expr\ expr                  \\
                       |\ & \CLam\ \mathcal{L}\ expr           \\
                       |\ & \CLet\ bind\ expr                  \\
                       |\ & \CCase\ expr\ \mathcal{L}\ [alt]   \\
                       |\ & \CType                             \\
    id\      \rightarrow\ & \CLocal\       \mathcal{L}         \\
                       |\ & \CGlobal\      \mathcal{G}         \\
                       |\ & \CConstructor\ \mathcal{D}         \\
    literal\ \rightarrow\ & \CLitNum\ \mathcal{N}              \\
                       |\ & \CLitStr\ \mathcal{S}              \\
    alt\     \rightarrow\ & \CAlt\ altcon\ expr\ [\mathcal{L}] \\
    altcon\  \rightarrow\ & \CDataAlt\ \mathcal{D}             \\
                       |\ & \CLitAlt\ literal                  \\
                       |\ & \CDefault                          \\
    bind\    \rightarrow\ & \CNonRec\ binder                   \\
                       |\ & \CRec\ [binder]                    \\
    binder   \rightarrow\ & \CBind\ \mathcal{L}\ expr
  \end{split}
\end{equation}
Where:
\begin{tabular}[t]{l @{ $=$ } l}
  $\mathcal{S}$ & string literals    \\
  $\mathcal{N}$ & numeric literals   \\
  $\mathcal{L}$ & local identifiers  \\
  $\mathcal{G}$ & global identifiers \\
  $\mathcal{D}$ & constructor identifiers
\end{tabular}
